---
title: "Example sites with blogdown"
date: "`r format(Sys.time(), '%B %d, %Y')`"
always_allow_html: yes
output:
  # for .tabset
  bookdown::html_document2:
  #html_document:
    code_folding: hide
    code_download: false
    toc: false
    toc_depth: 3
    # does this have an effect
    fig_caption: yes
    # this has no effect
    number_sections: yes
    # css: ['../_css/pandoc3.css', '../_css/myMargins.css']
csl: ../_csl/cell-numeric.csl
link-citations: true
---

```{css sidenote, echo = FALSE}

.main-container {
    margin-left: 250px;
}
.sidenote, .marginnote { 
  float: right;
  clear: right;
  margin-right: -40%;
  width: 37%;         # best between 50% and 60%
  margin-top: 0;
  margin-bottom: 0;
  font-size: 1.1rem;
  line-height: 1.3;
  vertical-align: baseline;
  position: relative;
  }
```


<style>
@import url('https://fonts.googleapis.com/css?family=Raleway');
@import url('https://fonts.googleapis.com/css?family=Oxygen');
@import url('https://fonts.googleapis.com/css?family=Raleway:bold');
@import url('https://fonts.googleapis.com/css?family=Oxygen:bold');

.main-container {
  max-width: 1400px !important;
}

body{
  font-family: 'Oxygen', sans-serif;
  font-size: 16px;
  line-height: 24px;
}

h1,h2,h3,h4 {
  font-family: 'Raleway', sans-serif;
}

.container { width: 1400px; }

caption {
  font-size: 20px;
  caption-side: top;
  text-indent: 30px;
  background-color: lightgrey;
  color: black;
  margin-top: 5px;
}

g-table-intro h4 {
  text-indent: 0px;
}
</style>


```{r setup, include = FALSE}

#options(knitr.duplicate.label = "allow")

knitr::opts_chunk$set(echo = TRUE,
                      comment = NA,
                      warning = FALSE,
                      error = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.width = 8,
                      fig.height = 4)
```

```{r infex-GlobalOptions, results="hide", include=FALSE, cache=FALSE}

knitr::opts_knit$set(stop_on_error = 2L) #really make it stop
options(knitr.table.format = 'html')

options(stringsAsFactors=F)

 #knitr::dep_auto()

```
<!-- ######################################################################## -->

```{r index-Prelims,  include=FALSE, echo=FALSE, results='hide', message=FALSE} 


FN <- "_example_sites"
if(sum(grepl(FN, list.files()))==0) stop("Check FN")

PREFIX <- "example_sites" 

 suppressMessages(require(rmarkdown))
 suppressMessages(require(knitr))

 suppressPackageStartupMessages(require(methods))
 suppressPackageStartupMessages(require(bookdown))

 suppressPackageStartupMessages(require(magrittr))

 # Shotcuts for knitting and rendering while in R session (Invoke interactive R from R/Scripts folder)
 kk <- function(n='') knitr::knit2html(paste("t", n, sep=''), envir=globalenv(),
       output=paste(FN,".html", sep=''))

 rr <- function(n='') rmarkdown::render(paste("t", n, sep=''), envir=globalenv(),
       output_file=paste(FN,".html", sep='')) ##, output_dir='Scripts')

 bb <- function(n='') browseURL(paste(FN,".html", sep=''))

 # The usual shortcuts
 zz <- function(n='') source(paste("t", n, sep=''))

 suppressPackageStartupMessages(require(magrittr))
```
<!-- ######################################################################## -->

<br/>

# Theme = `r h_theme  = "yihui/hugo-lithium"; h_theme` {.tabset}

URL: https://yihui-hugo-lithium.netlify.app/

## Home {-}

<br/>

## Structure {-}

```{r 1-initiate-site, echo=T, cache=T, cache.vars='h_theme_dir'}

h_theme_dir <- paste0("../", sub("/", '_', h_theme))

if(dir.exists(h_theme_dir)) fs::dir_delete(h_theme_dir)
dir.create(h_theme_dir)

blogdown::new_site(
       dir = h_theme_dir,
       theme = h_theme,
       force = NA,
       install_hugo = TRUE,
       format = "yaml",
       sample = TRUE,
       hostname = "github.com",
       theme_example = TRUE,
       empty_dirs = FALSE,
       to_yaml = TRUE,
       netlify = TRUE,
       .Rprofile = TRUE,
       serve = if (interactive()) "ask" else FALSE
     )
     

  
if(F)
t(t(list.files(h_theme_dir))) %>%
knitr::kable(
caption = "Content of site folders"
) 

fs::dir_tree(file.path(h_theme_dir), recurse=F)

```

### Detailed Structure {-}

```{r 1-det-struc}

fs::dir_tree(file.path(h_theme_dir), recurse=T)

```

<br/>

## config.yaml {-}

```{r 1-config-yaml, comment='', echo = F, cache=T, cache.vars=''}

file_content <- readLines(file.path(h_theme_dir,"config.yaml"))
cat(file_content, sep = "\n")

```


<br/>

## netlify.toml {-}

```{r 1-netlify-toml, comment='', echo = F, cache=T, cache.vars=''}

file_content <- readLines(file.path(h_theme_dir, "netlify.toml"))
cat(file_content, sep = "\n")

```

<br/>

## index.Rmd {-}


```{r 1-index-rmd, comment='', echo = F, cache=T, cache.vars=''}

file_content <- readLines(file.path(h_theme_dir, "index.Rmd"))
cat(file_content, sep = "\n")

```

<br/>

## R {.tabset -}

### build.R {-}

```{r 1-r-build-r, comment='', echo = F}

file_content <- readLines(file.path(h_theme_dir, "R/build.R"))
cat(file_content, sep = "\n")

```

<br/>

### build2.R {-}

```{r 1-r-build2-r, comment='', echo = F}
file_content <- readLines(file.path(h_theme_dir, "R/build.R"))
cat(file_content, sep = "\n")

```

<br/>

## content {-}

                  

```{r 1-content, comment='', echo = F}

fs::dir_tree(file.path(h_theme_dir, "content"))

```

<br/>

## Processing {- .tabset}

### Home {-}

<br/>


### Build {-}

* Use blogdown::serve_site() first to preview your site before building 
   - implements `LiveReload`

* Recommend running blogdown::check_content()

```{r 1-build, echo=T}

setwd(h_theme_dir)
blogdown::build_site()

fs::dir_tree(recurse=F)

```

* From local buid `output`, the `public` folder  can be ubloaded to
blogdown::serve_site()the Netlify drag-and-drop method

<br/>
<br/>



### Serve Locally {-}

To serve locally.

```{r 1-serve-site, echo = T}

options(servr.daemon = TRUE)

blogdown::serve_site(.site_dir = h_theme_dir)
	     
```

<br/>
<br/>

### A quick deploy {-}

<p><p/>
* **blogdown::serve_site()** first to preview your site before building it. 
   - By default, that function will knit your R Markdown content 

<p><p/>
* **blogdown::check_content()**. ... other things, we check if you have content that needs to be re-knit:
   - Checking your R Markdown content...
   - ○ All R Markdown files have been knitted.
   - ○ All R Markdown output files are up to date with their source files.
 
<p><p/>
* go online to Netlify Drop at https://app.netlify.com/drop
* drag and drop `public/`


<br/>
<br/>

### Automated deploy {-}

* have to host all source files of your website in a GIT repository
* follow Netlify  guide to create a new site from your GIT repository.
   - For a new site, you have to specify a command to build your website,
   - as well as the path of the publish directory.

* [yihui/hugo-lithium](https://yihui-hugo-lithium.netlify.app/)


<!--
* See [Netlify Doc: Configure Builds](https://docs.netlify.com/build/configure-builds/overview/)
--> 


<br/>
<br/>

# Theme = `r h_theme  = "yihui/hugo-xmin"; h_theme` {.tabset}

URL: https://yihui-hugo-xmin.netlify.app/

## Home {-}

<br/>

## Structure {-}

```{r 2-initiate-site, echo=T, cache=T, cache.vars='h_theme_dir'}
h_theme_dir <- paste0("../", sub("/", '_', h_theme))

if(dir.exists(h_theme_dir)) fs::dir_delete(h_theme_dir)
dir.create(h_theme_dir)

blogdown::new_site(
       dir = h_theme_dir,
       theme = h_theme,
       force = NA,
       install_hugo = TRUE,
       format = "yaml",
       sample = TRUE,
       hostname = "github.com",
       theme_example = TRUE,
       empty_dirs = FALSE,
       to_yaml = TRUE,
       netlify = TRUE,
       .Rprofile = TRUE,
       serve = if (interactive()) "ask" else FALSE
     )
     

  
if(F)
t(t(list.files(h_theme_dir))) %>%
knitr::kable(
caption = "Content of site folders"
) 

fs::dir_tree(file.path(h_theme_dir), recurse=F)

```


### Detailed Structure {-}

```{r 2-det-struc}

fs::dir_tree(file.path(h_theme_dir), recurse=T)

```

<br/>


<br/>

## hugo.yaml {-}

```{r 2-hugo-yaml, comment='', echo = F, cache=T, cache.vars=''}

file_content <- readLines(file.path(h_theme_dir,"hugo.yaml"))
cat(file_content, sep = "\n")

```


<br/>

## netlify.toml {-}

```{r 2-netlify-toml, comment='', echo = F, cache=T, cache.vars=''}

file_content <- readLines(file.path(h_theme_dir, "netlify.toml"))
cat(file_content, sep = "\n")

```

<br/>


## content {-}

```{r 2-content, comment='', echo = F}

fs::dir_tree(file.path(h_theme_dir, "content"))

```

<br/>

## Missing themes {}

- nanstats/tanka
- zwbetz-gh/cupper,
- alxschwar/simple-a
- jbub/ghostwriter



<br/>

# Theme = `r h_theme  = "xianmin/hugo-theme-jane"; h_theme` {.tabset}

URL: https://xianmin-hugo-theme-jane.netlify.app/

## Home {-}

<br/>

## Structure {-}

```{r 3-initiate-site, echo=T, cache=T, cache.vars='h_theme_dir'}

h_theme_dir <- paste0("../", sub("/", '_', h_theme))

if(dir.exists(h_theme_dir)) fs::dir_delete(h_theme_dir)
dir.create(h_theme_dir)

blogdown::new_site(
       dir = h_theme_dir,
       theme = h_theme,
       force = NA,
       install_hugo = TRUE,
       format = "yaml",
       sample = TRUE,
       hostname = "github.com",
       theme_example = TRUE,
       empty_dirs = FALSE,
       to_yaml = TRUE,
       netlify = TRUE,
       .Rprofile = TRUE,
       serve = if (interactive()) "ask" else FALSE
     )
     

  
if(F)
t(t(list.files(h_theme_dir))) %>%
knitr::kable(
caption = "Content of site folders"
) 

fs::dir_tree(file.path(h_theme_dir), recurse=F)

```


### Skip Detailed Structure {-}

```{r 3-det-struc,eval=F}

fs::dir_tree(file.path(h_theme_dir), recurse=T)

```

<br/>


<br/>

## hugo.yaml {-}

```{r 3-hugo-yaml, comment='', echo = F, cache=T, cache.vars=''}

file_content <- readLines(file.path(h_theme_dir,"hugo.yaml"))
cat(file_content, sep = "\n")

```


<br/>

## netlify.toml {-}

```{r 3-netlify-toml, comment='', echo = F, cache=T, cache.vars=''}

file_content <- readLines(file.path(h_theme_dir, "netlify.toml"))
cat(file_content, sep = "\n")

```

<br/>

## full-cinfig.toml {-}

```{r 3-full-config-toml, comment='', echo = F, cache=T, cache.vars=''}

file_content <- readLines(file.path(h_theme_dir, "full-config.toml"))
cat(file_content, sep = "\n")

```

<br/>



## content {-}

```{r 3-content, comment='', echo = F}

fs::dir_tree(file.path(h_theme_dir, "content"))

```

<br/>


```{r, echo=FALSE}
  knitr::knit_exit()
```


<!-- To run
# nohup Rscript -e "knitr::knit2html('_example_sites.Rmd')" > _example_sites.log  &

# Or
# nohup Rscript -e "rmarkdown::render('_example_sites.Rmd')" > _example_sites.log  &


-->


